\documentclass{article}
\usepackage{dirtytalk}


\begin{document}
\section*{Implemented changes}
\begin{itemize}
  \item The Sensibility analysis is now based on the maximum of the 2 norm, for a variable (but desecrate values of \(t\))
  \item The algorithm also calculates the time of the maximum (which could be used as relevant function for the sens.
    analysis)
  \item The ODE system has been corrected, s.t. it represents the ODE System of the paper correctly\\
        (I compared the plots to the Matlab plots in the paper)
  \item The Condition of the Experiment can be changed through variables similarly to the Matlab implementation.
\end{itemize}
\section*{Problems with the implementation}
\begin{itemize}
  \item ODEintWarning: Excess work done on this call \\
    \say{solved} by using \texttt{solve\_ivp}
  \item The restrictions on the number of sampling vectors in the master thesis seems incorrect.
    It says that the number of sampling vectors has to be a power-of two, while the cited paper says:
    \say{with N a sufficiently large number (500 or higher)} \\
    Additionally the paper notes that the cost of the analysis if \(N \cdot (k +2)\) where \(N\) is the number of
    Sampling vectors while the master thesis as far as I understand, denotes the number of Sampling vectors with \(k\) and as
    a result the formula \((2+n) * k\) \say{Modellauswertungen} also seems incorrect.\\
    The SAlib Package also accepts values of \(k\) which are not a power-of-two without any issues.
\end{itemize}
\section*{Questions for the parameters}
I copied the Intervals for the parameters from the master thesis, and only checked for the Parameters from Table 2 of the
Research paper. Should I also include the parameters from table 1 which were determined using sensitivity analysis? \\

The Intervals as far as I can tell have either been \(+- 25\%\) or standard deviation around the value, is there any reason
to this, especially in regards to when each of the methods is used?\\

In the Matlab Code there is a variable \texttt{degrinhi} which I did not find in the Paper, and therefore also have not
implemented. If I looked correctly the variable is also always set to 0, can I neglect it? \\
\end{document}
